A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-10 paper.tex
Updates from Overleaf

@@

\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
sentence. It might be appopriate to cite it elsewhere in the paper. Also,
there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
\todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
about the CPSed even-odd example?
I am confused about which paper to cite. \cite{herman2010space} seems to be citing
\cite{findler2002contracts} for the proxy-based approach of casting function.
Here is the relevant sentences from \cite{herman2010space}:
``In general, it is not possible to check if an untyped function satisfies a
particular static type. A natural solution is to wrap the function in a proxy that, whenever
it is applied, casts its argument and result values appropriately, ensuring that the function
is only observed with its expected type. This proxy-based approach was formalized by Findler
and Felleisen [15] ...''
I am \textit{not} trying to say I don't believe in your statements about the origins of
the proxy-based approach and blame tracking in functions.
I want to know whether \citet{herman2010space} is citing the right paper.
Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
is more related to our work.
}

\todo[inline]{JS: In the above you've lumped proxy-based and blame
  tracking together, which is incorrect. AFAIK,
  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
  You can read both papers for yourself and be the judge.  BTW, TAPL
  (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
  cited the wrong paper for function proxies, perhaps because they
  didn't know about \citet{Breazu-Tannen:1990vc}. Also,
  \cite{findler2002contracts} should have cited
  \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
  not consider that papers about ``casts'' to be closely related to
  their paper about ``contracts''.  Or perhaps they too did not know
  about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
  time regarding related work, and this is just yet another example of
  that. For that matter, I should have cited
  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
  probably because I had learned about it from TAPL and therefore
  thought it was so standard that it didn't need a citation.  But it
  would have been better for me to cite it.}

@@

\todo[inline]{KC: This paragraph suggests that
\cite{siek2009exploring} gives the definitional semantics.
\cite{siek2009exploring}'s is coercion-based.
It makes more sense to me to use a type-based semantics as the definition.
Actually in my mind \cite{siek2012interpretations} is definitional.}
\todo[inline]{JS: While I see what you're saying, its important
  to give precendence to the definition that is earlier in time.}

@@

	\fbox{$\mathrm{id}( T ) = c$}
	\[
	\begin{array}{rclr}
	\figequalto{id(\star)}{
		\hcci
	}{}
	\figequalto{id(P)}{
		\hccc{\hche}{id(P)}{\hcte}
	}{}
	\end{array}
	\]

	\fbox{$\mathrm{id}_m( P ) = m$}
	\[
	\begin{array}{rclr}
	\figequalto{id(\Pbool)}{\hcmbool}{}
	\figequalto{id(\Pfunc{S}{T})}{
		\hcmfunc{id(S)}{id(T)}
	}{}
	\figequalto{id(\Pprod{S}{T})}{
		\hcmprod{id(S)}{id(T)}
	}{}
	\end{array}
	\]

>>>>

\todo[inline]{KC: I feel ``going through a bisimulation proof'' is too specific.
There should be other ways to prove equivalence of two dynamic semantics.
How does Jeremy think?}

@@

% \todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
% \todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
% sentence. It might be appopriate to cite it elsewhere in the paper. Also,
% there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
% that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
% \todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
% about the CPSed even-odd example?
% I am confused about which paper to cite. \cite{herman2010space} seems to be citing
% \cite{findler2002contracts} for the proxy-based approach of casting function.
% Here is the relevant sentences from \cite{herman2010space}:
% ``In general, it is not possible to check if an untyped function satisfies a
% particular static type. A natural solution is to wrap the function in a proxy that, whenever
% it is applied, casts its argument and result values appropriately, ensuring that the function
% is only observed with its expected type. This proxy-based approach was formalized by Findler
% and Felleisen [15] ...''
% I am \textit{not} trying to say I don't believe in your statements about the origins of
% the proxy-based approach and blame tracking in functions.
% I want to know whether \citet{herman2010space} is citing the right paper.
% Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
% is more related to our work.
% }

% \todo[inline]{JS: In the above you've lumped proxy-based and blame
%   tracking together, which is incorrect. AFAIK,
%   \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
%   \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
%   You can read both papers for yourself and be the judge.  BTW, TAPL
%   (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
%   cited the wrong paper for function proxies, perhaps because they
%   didn't know about \citet{Breazu-Tannen:1990vc}. Also,
%   \cite{findler2002contracts} should have cited
%   \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
%   not consider that papers about ``casts'' to be closely related to
%   their paper about ``contracts''.  Or perhaps they too did not know
%   about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
%   time regarding related work, and this is just yet another example of
%   that. For that matter, I should have cited
%   \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
%   probably because I had learned about it from TAPL and therefore
%   thought it was so standard that it didn't need a citation.  But it
%   would have been better for me to cite it.}

@@

@@

	\fbox{$\mathrm{id}( T ) = c$}
	\[
	\begin{array}{rclr}
	\figequalto{\id{\star}}{
		\hcci
	}{}
	\figequalto{\id{P}}{
		\hccc{\hche}{\id{P}}{\hcte}
	}{}
	\end{array}
	\]

	\fbox{$\mathrm{id}_m( P ) = m$}
	\[
	\begin{array}{rclr}
	\figequalto{\id{\Pbool}}{\hcmbool}{}
	\figequalto{\id{\Pfunc{S}{T}}}{
		\hcmfunc{\id{S}}{\id{T}}
	}{}
	\figequalto{\id{\Pprod{S}{T}}}{
		\hcmprod{\id{S}}{\id{T}}
	}{}
	\end{array}
	\]
